### 2020-05-29 Report/aws_325ghz_study.tex
Smaller updates of the report.

@@

We will simply treat cases that matches a correction below a certain value as
``clear-sky''. If the correction limit is denoted as $dtb_{cs}$, the threshold
value, $x_{cs}$, is obtained by inverting the polynomial fit:
\begin{equation}
x_{cs} = f_{cs}^{-1}(dtb_{cs}) 
\label{eq:dtb}
\end{equation}
That is, if $x_m>x_{cs}$ a measurement is classified as clear-sky. If
$x_m\leq x_{cs}$, the measurement is rejected if a pure filtering is made, or
it is adjusted if the correction scheme is applied. We will largely set
$dtb_{cs}$ based on the noise level of the 183\,GHz channel involved, to be
1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitude of measurement
noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T). We will use $1\sigma$ for the development of the scheme, however, the sensitivity of the scheme to 1$\sigma$ and 2$\sigma$  threshold is also provided later in the text.

@@

To test the efficacy of the correction scheme, three different models: linear,
quadratic and cubic are evaluated to fit the TB differences between C1 and C2.
For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too
cloudy'' and are not corrected. Also, cases classified as clear according to $1\sigma$ threshold are not corrected. The clear-sky adjustment for all eligible
measurements is calculated from all three
models, and the three predicted datasets are compared.

@@

In Sec.~\ref{sec:validation} the validation of simulations against ATMS data
(Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were
underrepresented in comparison to the observations. In order to have a higher
representation of cloudy cases, we thinned the measurement dataset by removing
50\% of the clear-sky cases. Since the distribution of thinned dataset is more closer to real conditions, all the analyses presented further in this section are based on the thinned dataset.

@@

Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is
corrected using AWS-41. The TB differences for this combination and the cloud
impact in AWS-33 are highly correlated. Rejecting the cloudy cases reduces the
average bias in the measurements from -1.74\,K to -0.13\,K, while a correction
of cloudy cases reduces the bias further to 0.05\,K. The standard deviation and skewness of the corrected dataset are higher than pure-filtering, but smaller than the approach by  ``sreerekha et al''. Using $2\sigma$ threshold corrects a smaller fraction of cases than $1\sigma$ but the overall statistics are poorer in comparison to $1\sigma$, but still better than the ``sreerekha et al''.

@@

\section{Cloud correction by QRNN}
%
\dots

>>>>

[* Anders just informed us (May 29) that it would be good to avoid an IF of 1.7\,GHz, as that frequency could be used for downlink and there is a risk for
interference. The four channel option can easily be adopted to this, but what
do with the three channel one? *]

@@

We will simply treat cases that matches a correction below a certain value as
``clear-sky''. If the correction limit is denoted as $dtb_{cs}$, the threshold
value, $x_{cs}$, is obtained by inverting the polynomial fit:
\begin{equation}
x_{cs} = f_{cs}^{-1}(dtb_{cs}) 
\label{eq:dtb}
\end{equation}
That is, if $x_m>x_{cs}$ a measurement is classified as clear-sky. If
$x_m\leq x_{cs}$, the measurement is rejected if a pure filtering is made, or
it is adjusted if the correction scheme is applied. We will largely set
$dtb_{cs}$ based on the noise level of the 183\,GHz channel involved, to be
1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitude of measurement
noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T). We will use $1\sigma$ for
the development of the scheme, however, the sensitivity of the scheme to
a 1$\sigma$ or 2$\sigma$ threshold is also provided later in the text.

@@

To test the efficacy of the correction scheme, three different models: linear,
quadratic and cubic are evaluated to fit the TB differences between C1 and C2.
For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too
cloudy'' and are not corrected. Also, cases classified as clear according to
the $1\sigma$ threshold are not corrected. The clear-sky adjustment for all
eligible measurements is calculated from all three models, and the three
predicted datasets are compared.

@@

In Sec.~\ref{sec:validation} the validation of simulations against ATMS data
(Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were
underrepresented in comparison to the observations. In order to have a higher
representation of cloudy cases, we thinned the measurement dataset by removing
50\% of the clear-sky cases. The distribution of thinned dataset is more closer
to real conditions in the region matching weak cloud impacts and all the
analyses presented further in this section are based on the thinned dataset.

@@

Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is
corrected using AWS-41. The TB differences for this combination and the cloud
impact in AWS-33 are highly correlated. Rejecting the cloudy cases reduces the
average bias in the measurements from -1.74\,K to -0.13\,K, while a correction
of cloudy cases reduces the bias further to 0.05\,K. The standard deviation and
skewness of the corrected dataset are higher than pure-filtering, but smaller
than the approach by Sreerekha et al. Using $2\sigma$ threshold corrects a
smaller fraction of cases than $1\sigma$ but the overall statistics are poorer
in comparison to $1\sigma$, but still better than Sreerekha et al.

@@

\section{Cloud correction by QRNN}
%
There are two main drawbacks of the simple scheme introdoced in the previous
section. The filtering/correction only involves a single 325\,GHz channel. The
scheme could be extended to consider a higher number of channels, but there is
no obvious formulation of the expressions to apply. The second problem is that
no case-specific uncertainty estimate is provided, only the overal bias and
standard deviations are known. The first drawback hints towards using a machine
learning approach, and the second one suggests to use the special form denoted
QRNN (Quantile Regression Neural Network), that was introduced for ratmospheric
retrievals by \citet{pfreundschuh:aneur:18}.
